---
output: 
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## mcap

The goal of `mcap` is to provide a model-based clustering approach in very high 
dimensions (especially when $p \gg n$) via adaptive projections.
Clustering is based on Gaussian mixture models in a lower dimensional (projected) space.
Projection dimension is set adaptively based on a cluster stability criterion.
Available projection variants (so far) include PCA and Random Projections.

### Resources
See our paper: ...


### Getting Started
Clone or download the [code](https://github.com/btaschler/MCAP) from github.

Alternatively, you can install `mcap` directly from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("btaschler/MCAP")
```


### Prerequisites

Dependencies on other packages:
- `huge`
- `pcaMethods`
- `nethet`
- ...


```
[ ... examples ... ]
```


### Quick demo

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


Using the Gram matrix to compute PCA components: Input matrix $X \sim \text{MVN}(0,1)$, 
output matrix $Z$ consists of the first $npc = 2$ principal components.
```{r}
library(mcap)
X <- matrix(rnorm(2000),20,100)
Z <- GramPCA(X, npc = 2)
print(Z)
```



### Running the tests
```{r tests}
## basic example code
```


### Versioning

We use [Semantic Versioning](http://semver.org/) for versioning. For the versions available, see the [tags on this repository](https://github.com/btaschler/MCAP/releases). 


### Authors

* **Bernd Taschler, Sach Mukherjee** -- *Initial work* -- [BT](https://github.com/btaschler)

See also the list of [contributors](https://github.com/btaschler/MCAP/graphs/contributors) who participated in this project.


### License

This project is licensed under the GNU General Public License -- see the [LICENSE.md](LICENSE.md) file for details.


### Acknowledgments

* Konstantinos Perrakis for valuable discussions.


